Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
Minor

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art results \todo{Could add a noun after state-of-the-art} on CL benchmarks. However, they are limited to using subset approximations of the posterior. Instead, we use the sparse data term posterior, see \cref{app:cl} for details.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
\our is a more principled approach since the resultant GP is a low-rank approximation of the full data which ensures information is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from

@@

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview
We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}). We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.
% Benchmarks/architectures
 Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST). We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency. Please refer to \cref{app:cl-exp} for full details.

@@

% Discussion points
In practical terms, our model serves a role similar to a sparse GP. However, unlike a conventional GP, it does not provide a straightforward method for specifying or tuning the prior covariance function. This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify and tune the prior assumptions, thereby incorporating a broad range of inductive biases into the model. It is important to note that the NTK linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.

>>>>

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art \todo{Could add a noun after state-of-the-art} on CL benchmarks. However, they are limited to using subset approximations of the posterior. Instead, we use the sparse data term posterior, see \cref{app:cl} for details.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
\our is a more principled approach since the resultant GP is a low-rank approximation of the full data which ensures information is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from

@@

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview
We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}). We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
%
% Benchmarks/architectures
 Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST). We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency. Please refer to \cref{app:cl-exp} for full details.

@@

% Discussion points
In practical terms, our model serves a role similar to a sparse GP. However, unlike a conventional GP, it does not provide a straightforward method for specifying or tuning the prior covariance function. This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify and tune the prior assumptions, thereby incorporating a broad range of inductive biases into the model. It is important to note that the Laplace-GGN approach linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.\looseness-1
